---
title: "closer_look_MLM5&MLM6"
author: "Yoo Ri Hwang"
date: '2022-07-01'
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
## Overview

MLM5: gender composition (ff mm mixed) without interaction
MLM6 gender composition (FF mm mixed) with interaction 

Under certain conditions, it shows 100% of singularity and 0 pseudo ICC in MLM5 and MLM6. 
In this document, we attempt to get closer look into how generated data are fitted into MLM5 and MLM6. 

So, this is NOT main documents. 

## load package 
```{r}

library(tidyverse)

source('scripts/gen_dyadic.R')
source('scripts/gen_rmvn.R')
source('scripts/dyad_to_long.R')
source('scripts/reconstruct.R')
source('scripts/model_sib.R')
source('scripts/model_null.R')
source('scripts/model_mlm.R')
source('scripts/ICC_calculator.R')
source('scripts/myTryCatch.R')
source('scripts/hasConverged.R')
```


### Table
```{r}

#overall singularity rate and psuedoICC across all multilevel model 
table<-read.csv("appendix/singularity_with_psuedoICC.csv")

# pick mlm5 and mlm 6

mlm56<-table[,grep("CN|beta|condition|ICC|MLM5|MLM6",names(table))]
```

## generate raw dataset, and fit into MLM5 and MLM6

### data generated per each condition (one dataset per one condition) 
117 conditions
```{r}
set.seed(5)
# condition information


conditions<-read.csv("conditions/Conditions_summary.csv")
ncond<-nrow(conditions)

# empty holder to put generated dataset


dyad_data<-vector(mode = "list", length = ncond)

### generate the data 

for (j in 1:ncond) {

  
    sim_data <- gen_dyadic(
    cn = conditions$cn[j],
    beta1 = conditions$beta1[j],
    beta2 = conditions$beta2[j],
    beta3 = conditions$beta3[j],
    con_icc_wtn = conditions$wtn[j],
    con_icc_btw = conditions$btw[j],
    cat_icc_wtn = conditions$wtn[j],
    cat_icc_btw = conditions$btw[j])
    
    dyad_data[[j]]<-sim_data
}


## holder  for generated data so that I can keep the data
ind_data<-vector(mode = "list", length = ncond)


# dyad_data has dyadic structure. let's convert it into individual structure so that I can run multilevel model

for(i in 1:ncond){
ind_data[[i]]<-dyad2ind(dyad_data[[i]])
}
```
### fit that into MLM5 and MLM6 

```{r}
# empty holder for generated data 

MLM5<-vector("list",length=ncond)
MLM6<-vector("list",length=ncond)
sum_MLM5<-vector("list",length=ncond)
sum_MLM6<-vector("list",length=ncond)

## fit the data into the models (MLM5, MLM6)

for(i in 1:ncond){

MLM5[[i]]<- yes2model(data=ind_data[[i]],
                gender_composition=3,
                interaction=FALSE)

MLM6[[i]]<- yes2model(data=ind_data[[i]],
                gender_composition=3,
                interaction=TRUE)
print(paste0(i," MLM5 cn:",conditions$cn[i]," ticc: ",conditions$target_ICC[i]," b2:",conditions$beta2[i]," b3:",conditions$beta3[i]))
print(sum_MLM5[[i]]<-summary(MLM5[[i]]))

print(paste0(i," MLM6 cn:",conditions$cn[i]," ticc: ",conditions$target_ICC[i]," b2:",conditions$beta2[i]," b3:",conditions$beta3[i]))
print(sum_MLM6[[i]]<-summary(MLM6[[i]]))
}


```
