---
title: "results"
author: "Yoo Ri Hwang"
date: '2022-07-11'
output: html_document
---

# Overview

This document is to generate tables/plots for manuscripts. 

some codes for saving the tables were commentised so that it does not overwrite.
sig rate is significance rate. 


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Pacakges 

```{r}

library(tidyverse)
library(openxlsx) # for xlsx output 
library(latex2exp) # so that I can put some latex in my plots 

library(kableExtra)
library(flextable)
library(rempsyc)

```

#singularity table

```{r}

# read the data 

sin<-read.csv("appendix/singularity.csv")

# MLM5 and MLM6 showed 100% of singuarity rates, so grab it.

sin<-sin[,grep("MLM5|MLM6|beta|ICC|CN",names(sin))]

sin2<-sin %>%
  subset(singularity_MLM5==1 | singularity_MLM6==1)

sin2<- sin2[,c(3,5:7)]
nt<-nice_table(sin2, 
           title = c("The conditions where MLM5 and MLM6 shows 100% of singularity rate"))
nt <- nt %>%
  autofit()

#save_as_docx(nt, path = "tables/singularity.docx")


```

# Table for type 1 error rate 

Regarding Type 1 error rate, the 0 ~ 2.5% and 7.5% ~ 100% were especially catch the author's attention. 
## gender type 1 error rate
```{r}

# read data 
g<-read.csv('type1error/beta2.csv')

# take only what we need for this table
mean<-read.csv('descriptive_results/mean_var.csv')
mean<-mean[,grep("condition|mean",names(mean))]
mean<-mean[,grep("condition|ev|two|catwtn|catbtw", names(mean))]
mean<-mean[,-grep("_t_|_p_|_se_|level|Dev",names(mean))]

g2<-g[,-grep("fx|nx",names(g))]
gmean<-mean[,-grep("fx|nx",names(mean))]

g2<-merge(g2,gmean, key="condition")

#write.csv(g2,'tables/appendix1_type1error_gender.csv')

```

# type 1 error rate for interaction type 1 error 
```{r}

# read the data 
s<-read.csv('type1error/beta3.csv')


#sib2, sib3, MLM4 MLM 6


# sib 2

# take only what we need

s<-s[,grep("coef|condition|beta|ICC|CN",names(s))]
sib2<- s[,grep("sib2|condition|beta|ICC|CN",names(s))]

inmean<-mean[,grep("condition|nx|fx", names(mean))]

sib2mean<-inmean[,grep("condition|sib2", names(inmean))]


sib2<-sib2 %>%
  filter(if_any(starts_with("coef"), ~.>= 0.075) |if_any(starts_with("coef"), ~.<= 0.025))


sib2<-merge(sib2,sib2mean,key="condition")
                
#write.csv(sib2, file="tables/type1error_interaction_sib2.csv")

# sib3



# take only what we need 
sib3<- s[,grep("sib3|condition|beta|ICC|CN",names(s))]

sib3<-sib3 %>%
  filter(if_any(starts_with("coef"), ~.>= 0.075) |if_any(starts_with("coef"), ~.<= 0.025))


sib3mean<-inmean[,grep("condition|sib3", names(inmean))]
sib3<-merge(sib3,sib3mean,key="condition")

#write.xlsx(sib3, sheetName="sheet1", file="tables/type1error_interaction_sib3.xlsx")

# MLM4

#take only what we need 

MLM4<- s[,grep("MLM4|condition|beta|ICC|CN",names(s))]

MLM4<-MLM4 %>%
  filter(if_any(starts_with("coef"), ~.>= 0.075) |if_any(starts_with("coef"), ~.<= 0.025))


MLM4mean<-inmean[,grep("condition|MLM4", names(inmean))]
MLM4<-merge(MLM4,MLM4mean,key="condition")



#write.xlsx(MLM4, sheetName="sheet1", file="tables/type1error_interaction_MLM4.xlsx")

# MLM6 
# take only what we need 


MLM6<- s[,grep("MLM6|condition|beta|ICC|CN",names(s))]

MLM6<-MLM6 %>%
  filter(if_any(starts_with("coef"), ~.>= 0.075) |if_any(starts_with("coef"), ~.<= 0.025))



MLM6mean<-inmean[,grep("condition|MLM6", names(inmean))]
MLM6mean<-MLM6mean[,-grep("df", names(MLM6mean))]

MLM6<-merge(MLM6,MLM6mean,key="condition")


#write.xlsx(MLM6, sheetName="sheet1", file="tables/type1error_interaction_MLM6.xlsx")
```

## table for power

```{r}

# we only get the info of sig rate for MLM4, where there is interaction effect! 

p<-read.csv('type1error/MLM4_sig_rate.csv')

p <- p %>%
  filter(beta3 !=0)


```

# table for overfitting problem

```{r}
# read the data 
ov<-read.csv('appendix/singularity_with_psuedoICC.csv')
# digits 
options(scipen=999)
# tale when the singurarity rate is 100 % 
ov<-ov %>%
    filter(if_any(starts_with("singularity"), ~.==1))

#write.xlsx(ov, sheetName="sheet1", file='appendix/singularity100ICC.xlsx')

```

# plots for type 1 error rate

## Data management 
```{R}

beta3<-read.csv("type1error/beta3.csv")
beta3$X<-NULL
beta3$beta3_factor<-as.factor(beta3$beta3)
beta3$beta2_factor<-as.factor(beta3$beta2)
beta3$ICC_factor<-as.factor(beta3$ICC)
beta3$CN_factor<-as.factor(beta3$CN)

beta3_long <- beta3 %>%
  pivot_longer( cols=-c("beta1","condition","beta2","beta3","ICC","CN","beta2_factor",
                        "beta3_factor","ICC_factor","CN_factor"),
    names_to = c('coef', 'model1'),
               names_sep = '(?<=_p_)')

beta3_long<-beta3_long %>%
  mutate(model = case_when(
    model1=="sib0"~"REG0",
    model1=="sib1"~"REG1",
    model1=="sib2"~"REG2",
    model1=="sib3"~"REG3",
    model1=="MLM0"~"MLM0",
    model1=="MLM1"~"MLM1",
    model1=="MLM2"~"MLM2",
    model1=="MLM3"~"MLM3",
    model1=="MLM4"~"MLM4",
    model1=="MLM5"~"MLM5",
    model1=="MLM6"~"MLM6"
  ))



beta3_list <- beta3_long %>% 
  group_split(model)

MLM4<-beta3_list[[2]]
MLM6<-beta3_list[[3]]

reg2<-beta3_list[[4]]
reg3<-beta3_list[[5]]

```
## Reg2 interaction type1 error rate
```{r}


  reg2_type1<-ggplot(reg2, 
            aes(y= value, 
                x= coef,
                colour=beta2_factor) 
  )+
    geom_point(alpha=0.4, size=5) +
     facet_grid(ICC~CN,
                     labeller="label_both")  +
   scale_colour_brewer(palette="OrRd") +
    
    theme(panel.background= element_rect(fill = "grey"),axis.title.x=element_blank(),
          axis.title.y=element_blank()
          )+
    geom_hline(yintercept=0.025, linetype="dashed")+
   geom_hline(yintercept=0.075, linetype="dashed")+
    labs(colour="beta2")+
    scale_x_discrete("coef",
                     labels=c("coef_con_diffxgender_composition_two_eff_p_"= TeX("$\\beta_{5}$"))
                     )

library(apaTables)
reg2$ICC_factor <- relevel(as.factor(reg2$ICC_factor), ref="0.2")
reg2$beta2_factor <- relevel(as.factor(reg2$beta2_factor), ref="0")
reg2$CN_factor <- relevel(as.factor(reg2$CN_factor), ref="30")

reg2lm<-lm(value~CN_factor+beta2_factor+ICC_factor,reg2)
reg21s<-summary(reg2lm)
round(reg21s[["coefficients"]],digits=2)
print(summary(reg2lm)$coefficients,digits=1)
apa.reg.table(reg2lm,filename="sib2model_interaction_type1_regressio.doc")
```

## Reg3 type 1 error rate of interaction

```{r}


  reg3_type1<-ggplot(reg3, 
            aes(y= value, 
                x= coef,
                colour=beta2_factor) 
  )+
    geom_point(alpha=0.4, size=5) +
     facet_grid(ICC~CN,
                     labeller="label_both")  +
   scale_colour_brewer(palette="OrRd") +
    
    theme(panel.background= element_rect(fill = "grey"),axis.title.x=element_blank(),
          axis.title.y=element_blank()
          )+
       geom_hline(yintercept=0.025, linetype="dashed")+
   geom_hline(yintercept=0.075, linetype="dashed")+
    labs(colour="beta2")+
    scale_x_discrete("coef",
                     labels=c("coef_con_diffxev1_p_"= TeX("$\\beta_{6}$"),
                              "coef_con_diffxev2_p_"= TeX("$\\beta_{7}$")
                                                          ))
                    
reg3$ICC_factor <- relevel(as.factor(reg3$ICC_factor), ref="0.2")
reg3$beta2_factor <- relevel(as.factor(reg3$beta2_factor), ref="0")
reg3$CN_factor <- relevel(as.factor(reg3$CN_factor), ref="30")

reg3lm<-lm(value~CN_factor+beta2_factor+ICC_factor,reg3)
round(summary(reg3lm)[["coefficients"]],digits=2)
print(summary(reg3lm)$coefficients,digits=2)
apa.reg.table(reg3lm,filename="sib3model_interaction_type1_regressio.doc")
```
###type 1 error plot for mlm 4

```{r}



  MLM4_type1<-ggplot(MLM4, 
            aes(y= value, 
                x= coef,
                colour=beta2_factor) 
  )+
    geom_point(alpha=0.4, size=5) +
     facet_grid(ICC~CN,
                     labeller="label_both")  +
   scale_colour_brewer(palette="OrRd") +
    
    theme(panel.background= element_rect(fill = "grey"),axis.title.x=element_blank(),
          axis.title.y=element_blank()
          )+
    geom_hline(yintercept=0.025, linetype="dashed")+
   geom_hline(yintercept=0.075, linetype="dashed")+
    labs(colour="beta2")+
    scale_x_discrete("coef",
                     labels=c("coef_fixed_conxcatbtw_p_"= TeX("$\\gamma_{11}$"))
                     )
  MLM4_type1
```

### type 1 error rate of MLM6
```{r}

  MLM6_type1<-ggplot(MLM6, 
            aes(y= value, 
                x= coef,
                colour=beta2_factor) 
  )+
    geom_point(alpha=0.4, size=5) +
     facet_grid(ICC~CN,
                     labeller="label_both")  +
   scale_colour_brewer(palette="OrRd") +
    
    theme(panel.background= element_rect(fill = "grey"),axis.title.x=element_blank(),
          axis.title.y=element_blank()
          )+
       geom_hline(yintercept=0.025, linetype="dashed")+
   geom_hline(yintercept=0.075, linetype="dashed")+
    labs(colour="beta2")+
    scale_x_discrete("coef",
                     labels=c("coef_fixed_conxev1_p_"= TeX("$\\gamma_{11}$"),
                              "coef_fixed_conxev2_p_"= TeX("$\\gamma{12}$")
                                                          ))
            
                
MLM6$ICC_factor <- relevel(as.factor(MLM6$ICC_factor), ref="0.2")
MLM6$beta2_factor <- relevel(as.factor(MLM6$beta2_factor), ref="0")
MLM6$CN_factor <- relevel(as.factor(MLM6$CN_factor), ref="30")

MLM6lm<-lm(value~CN_factor+beta2_factor+ICC_factor,MLM6)
round(summary(MLM6lm)[["coefficients"]],digits=2)
print(summary(MLM6lm)$coefficients,digits=2)
apa.reg.table(MLM6lm,filename="MLM6model_interaction_type1_regressio.doc")

MLM6_type1
```

## power plot (MLM4)

## Datamanagement


## load the data

```{r data}

sig_rate<-read.csv("type1error/sig_rate_with_conditions.csv")

```


```{r cleaning}
# 
sig_rate$X<-NULL
sig_rate$X.1<-NULL



sig_rate$beta2_factor<-as.factor(sig_rate$beta2)
sig_rate$beta3_factor<-as.factor(sig_rate$beta3)
sig_rate$ICC_factor<-as.factor(sig_rate$ICC)
sig_rate$CN_factor <- as.factor(sig_rate$CN)



### data reshaping for plotting  for 0.05 alpha 

# wide to long 
sig_rate_long<-sig_rate%>%
  pivot_longer( cols=-c("beta1","condition","beta2","beta3","ICC","CN",
                        "beta2_factor","beta3_factor","ICC_factor","CN_factor"),
    names_to = c('coef', 'model1'),
               names_sep = '(?<=_p_)')


sig_rate_long<-sig_rate_long %>%
  mutate(model = case_when(
    model1=="sib0" ~ "REGNTW",
    model1=="sib1" ~ "REGNTH",
    model1=="sib2" ~ "REGYTW",
    model1=="sib3" ~ "REGYTH",
    model1=="MLM0" ~ "MLM0",
    model1=="MLM1" ~ "MLMNID",
    model1=="MLM2" ~ "MLMYID",
    model1=="MLM3" ~ "MLMNTW",
    model1=="MLM4" ~ "MLMYTW",
    model1=="MLM5" ~ "MLMNTH",
    model1=="MLM6" ~ "MLMYTH"
  ))



sig_rate_long <- sig_rate_long %>%
  mutate(
    correspond = case_when(
      coef=="coef_con_diff_p_" ~ "edu_within",
      coef=="coef_con_diffxev1_p_" ~ "interaction",
      coef=="coef_con_diffxev2_p_" ~ "interaction",
      coef=="coef_con_diffxgender_composition_two_eff_p_" ~ "interaction",
      coef=="coef_con_mean_p_" ~ "edu_between",
      coef=="coef_ev1_p_" ~ "gender_between",
      coef=="coef_ev2_p_" ~ "gender_between",
      coef=="coef_fixed_catbtw_p_" ~ "gender_between",
      coef=="coef_fixed_catwtn_p_" ~ "gender_within",
      coef=="coef_fixed_catwtnxcon_p_"  ~ "interaction",
      coef=="coef_fixed_con_p_" ~ "edu_within",
      coef=="coef_fixed_conxcatbtw_p_" ~ "interaction",
      coef=="coef_fixed_conxev1_p_" ~ "interaction",
      coef=="coef_fixed_conxev2_p_" ~ "interaction",
      coef=="coef_fixed_ev1_p_" ~ "gender_between",
      coef=="coef_fixed_ev2_p_" ~ "gender_between",
      coef=="coef_fixed_Intercept_p_" ~ "intercept",
      coef=="coef_gender_composition_two_eff_p_"~"gender_between",
      coef=="coef_intercept_p_" ~ "intercept",
      coef=="coef_y_mean_p_" ~ "health_between",
      coef=="f_p_" ~ "F_test_dyadic"
    )
  )




sig_rate_long2_interaction <- sig_rate_long %>%
  mutate(
    correspond = case_when(
      
      coef=="coef_con_diffxev1_p_" ~ "edudiffxinteraction_ev1",
      coef=="coef_con_diffxev2_p_" ~ "edudiffxinteraction_ev2",
      coef=="coef_con_diffxgender_composition_two_eff_p_" ~ "edu_diffxgendercomposition_two",
     
      coef=="coef_fixed_catwtnxcon_p_"  ~ "education_genderwithin",
      
      coef=="coef_fixed_conxcatbtw_p_" ~ "eduxgendercomposition_two",
      coef=="coef_fixed_conxev1_p_" ~ "eduxinteraction_ev1",
      coef=="coef_fixed_conxev2_p_" ~ "edudiffxinteraction_ev2",
      TRUE ~ NA_character_
      
    )
  )


# I tried to draw big giant plot, but r says thare are restrictions ( maximum number of points/ maximum number of levels) so, let's split a data. that's not an ideal way to do so, but R is not not perfect

## by sample size 
sig_rate_long_CN30<- sig_rate_long %>%
  subset(CN==30)
sig_rate_long_CN120<- sig_rate_long %>%
  subset(CN==120)
sig_rate_long_CN510<- sig_rate_long %>%
  subset(CN==510)



# by corresponds 

sig_rate_long_edu_between<- sig_rate_long %>%
  subset(correspond=="edu_between")
sig_rate_long_edu_within<- sig_rate_long %>%
  subset(correspond=="edu_within")
sig_rate_long_F_test_dyadic<- sig_rate_long %>%
  subset(correspond=="F_test_dyadic")
sig_rate_long_gender_between<- sig_rate_long %>%
  subset(correspond=="gender_between")
sig_rate_long_gender_within<- sig_rate_long %>%
  subset(correspond=="gender_within")
sig_rate_long_health_between<- sig_rate_long %>%
  subset(correspond=="health_between")
sig_rate_long_interaction<- sig_rate_long %>%
  subset(correspond=="interaction")
sig_rate_long_intercept<- sig_rate_long %>%
  subset(correspond=="intercept")

#closer compare for interaction effect 


```

```{r}


sig_rate9 <- sig_rate %>%
  subset( beta3!=0)

  
 ggplot(sig_rate9, aes(y= coef_fixed_conxcatbtw_p_MLM4, 
                          x= ICC, 
                          colour = beta3_factor, 
                          size = beta2))+
        geom_point(alpha=0.45) +
       labs(colour="beta3")+
          facet_wrap(~CN, labeller="label_both") +
   scale_colour_brewer(palette="OrRd") + 
      ylab("MLM4")+
  scale_size_continuous(breaks=c(0,0.1,0.3,0.5)) +
   theme(panel.background= element_rect(fill = "grey"))+
   geom_hline(yintercept=0.05, linetype="dashed")+
   geom_hline(yintercept=0.80, linetype="dashed")
   
 

```
# APPENdix  ( the sig rate of the parameters)

The sig rate of parameters (under 0.05 alpha level) were plotted, according to the parameters (the parameters that corresponds to either education effect, gender effect, or interaction effect)


```{r}

## edu-between
  ggplot(sig_rate_long_edu_between, 
             aes(y= value, x= model, 
                 colour = beta3_factor, 
                 size = beta2))+
        geom_point(alpha=0.45) +
     facet_grid(ICC~CN, labeller="label_both") +
   scale_colour_brewer(palette="OrRd") + 
  labs(colour="beta3")+
   theme(panel.background= element_rect(fill = "grey"))+
   geom_hline(yintercept=0.05, linetype="dashed")+
   geom_hline(yintercept=0.80, linetype="dashed")+
  theme(axis.text.x = element_text(angle = 70, hjust=1))+
  theme(axis.title.x = element_blank(),
          axis.title.y = element_blank())+
   scale_size_continuous(breaks=c(0,0.1,0.3,0.5)) +
  theme(plot.margin = margin(0.6, 0.6, 0.6, 0.6, "cm")) +
  ggtitle("Between-dyad effects of education")
  
```

```{r}

# edu_within


ggplot(sig_rate_long_edu_within, 
             aes(y= value, 
                 x= model, 
                 colour = beta3_factor, 
                 size = beta2))+
        geom_point(alpha=0.45) +
           facet_grid(ICC~CN, labeller="label_both") +
  labs(colour="beta3")+
   scale_colour_brewer(palette="OrRd") + 
   theme(panel.background= element_rect(fill = "grey"))+
   geom_hline(yintercept=0.05, linetype="dashed")+
   geom_hline(yintercept=0.80, linetype="dashed")+
  theme(axis.text.x = element_text(angle = 70, hjust=1))+
     scale_size_continuous(breaks=c(0,0.1,0.3,0.5)) +
  theme(plot.margin = margin(0.6, 0.6, 0.6, 0.6, "cm")) +
   theme(axis.title.x = element_blank(),
          axis.title.y = element_blank())+
  ggtitle("Within-dyad effect of education")

# f-test for dyadic regression

ggplot(sig_rate_long_F_test_dyadic, 
             aes(y= value, 
                 x= model,
                  
                 colour = beta3_factor, 
                 size = beta2))+
        geom_point(alpha=0.45) +
            facet_grid(ICC~CN, labeller="label_both") +
   labs(colour="beta3")+
   scale_colour_brewer(palette="OrRd") + 
   theme(panel.background= element_rect(fill = "grey"))+
   geom_hline(yintercept=0.05, linetype="dashed")+
   geom_hline(yintercept=0.80, linetype="dashed")+
  theme(axis.text.x = element_text(angle = 75,  hjust=1))+
   scale_size_continuous(breaks=c(0,0.1,0.3,0.5)) +
  theme(plot.margin = margin(0.6, 0.6, 0.6, 0.6, "cm")) +
   theme(axis.title.x = element_blank(),
          axis.title.y = element_blank())+
  ggtitle("p-value for the F-test in regression")

# gender_Between 
ggplot(sig_rate_long_gender_between, 
             aes(y= value, x= model, 
                  
                 colour = beta3_factor, 
                 size = beta2))+
        geom_point(alpha=0.45) +
   labs(colour="beta3")+
          facet_grid(ICC~CN, labeller="label_both") +
   scale_colour_brewer(palette="OrRd") + 
   theme(panel.background= element_rect(fill = "grey"))+
   geom_hline(yintercept=0.05, linetype="dashed")+
   geom_hline(yintercept=0.80, linetype="dashed")+
  theme(axis.text.x = element_text(angle = 75,  hjust=1))+
   scale_size_continuous(breaks=c(0,0.1,0.3,0.5)) +
  theme(plot.margin = margin(0.6, 0.6, 0.6, 0.6, "cm")) +
   theme(axis.title.x = element_blank(),
          axis.title.y = element_blank())+
  ggtitle("Gender-composition effects")


#gender_within

ggplot(sig_rate_long_gender_within, 
             aes(y= value, x= model, 
                  
                 colour = beta3_factor, 
                 size = beta2))+
        geom_point(alpha=0.45) +
           facet_grid(ICC~CN, labeller="label_both") +
   scale_colour_brewer(palette="OrRd") + 
   theme(panel.background= element_rect(fill = "grey"))+
   geom_hline(yintercept=0.05, linetype="dashed")+
   geom_hline(yintercept=0.80, linetype="dashed")+
  theme(axis.text.x = element_text(angle = 75,  hjust=1))+
   labs(colour="beta3")+
   scale_size_continuous(breaks=c(0,0.1,0.3,0.5)) +
  theme(plot.margin = margin(0.6, 0.6, 0.6, 0.6, "cm")) +
   theme(axis.title.x = element_blank(),
          axis.title.y = element_blank())+
  ggtitle("Individual gender effect")

# interaction 
ggplot(sig_rate_long_interaction, 
             aes(y= value, 
                 x= model, 
                 colour = beta3_factor, 
                 size = beta2))+
        geom_point(alpha=0.4) +
          facet_grid(ICC~CN, labeller="label_both") +
   scale_colour_brewer(palette="OrRd") + 
   labs(colour="beta3")+
    theme(panel.background= element_rect(fill = "grey"),axis.title.x=element_blank(),
          axis.title.y=element_blank()
          ) +
   geom_hline(yintercept=0.05, linetype="dashed")+
   geom_hline(yintercept=0.80, linetype="dashed")+
  theme(axis.text.x = element_text(angle = 75, hjust=1))+
  theme(plot.margin = margin(0.6, 0.6, 0.6, 0.6, "cm")) +
   scale_size_continuous(breaks=c(0,0.1,0.3,0.5)) +
   theme(axis.title.x = element_blank(),
          axis.title.y = element_blank())+
  ggtitle("Interaction effect")

```


### Apendix

```{r}

sig_rate<-read.csv('type1error/sig_rate.csv')

condition <-read.csv('conditions/Conditions_summary.csv')
condition <- condition[,grep("cn|ICC|beta|condition",names(condition))]
sig_rate<-sig_rate[,grep("con|ev|gender|catwtn|condition|catbtw",names(sig_rate))]
sig_rate<-sig_rate[,-grep("mean",names(sig_rate))]

Ap_sig<-merge(condition,sig_rate, key="condition")
#write.csv(Ap_sig, 'tables/appendix_sig_rate.csv')

reg_sig_rate<-Ap_sig[,grep("sib|condition|CN|beta|ICC|catbtw",names(Ap_sig))]
reg_sig_rate<-round(reg_sig_rate,digits=2)
#write.csv(reg_sig_rate, 'tables/appendix_sig_rate_reg.csv')


mlm_sig_rate<-Ap_sig[,grep("MLM|condition|CN|beta|ICC|catbtw",names(Ap_sig))]
mlm_sig_rate<-round(mlm_sig_rate,digits=2)
#write.csv(mlm_sig_rate, 'tables/appendix_sig_rate_MLM.csv')

```
